Pricing Approaches for Green Tea Products

### 2024-11-21 paper/paper.qmd
Updated figure caption and label to be more informative

---
title: "Pricing Approaches for Green Tea Products"
subtitle: "A Study of Canadian Grocery Retailers"
author: 
  - David Qi
  - Haobo Ren
  - Xinrui Xie
  - Ruikang Wang
  - Sakura Hu
thanks: "Code and data are available at: https://github.com/UTDQi/grocery_analysis"
date: today
date-format: long
abstract: "This study uses canadian grocery Price data to analyzes the pricing strategies of green tea-related products across grocery stores in Canada. We finds T&T offers a mix of premium and affordable teas, targeting its Asian customer base, while Walmart maintains low prices through economies of scale. Loblaws uses dynamic pricing and promotions to attract budget-conscious consumers. These strategies reflect different approaches to catering to diverse consumer segments."
format: pdf
number-sections: true
toc: true
bibliography: references.bib
---

@@

library(tidyverse)
library(ggplot2)

@@

## Overview
[@fig-PriceVsVendor] is a graph showing the overall distribution for price of green tea related products for each vendor. The term average price refers to the mean price of a product observed over the time where data is available.
Most vendors exhibit a right-skewed distribution in green tea related product prices, with the majority priced on the lower end of the spectrum. This pattern suggests that, while there are some high-priced teas, they are relatively uncommon compared to more affordable options.
```{r}
#| label: fig-PriceVsVendor
#| fig-cap: Distribution of Average Prices by Vendor
#| include: true
#| echo: false
#| warning: false
#| message: false

@@

```{r}
#| label: fig-ChangeInGinsengLemon
#| fig-cap: Price Change of Lipton Ginseng Lemon Green Tea 72 Counts
#| include: true
#| echo: false
#| warning: false
#| message: false

# Ensure `nowtime` is in datetime format and `current_price` is numeric
price_change$nowtime <- as.POSIXct(price_change$nowtime)
price_change$current_price <- as.numeric(price_change$current_price)

# Sample ggplot code to create the point graph
ggplot(price_change, aes(x = nowtime, y = current_price, color = vendor)) +
  geom_point(alpha = 0.6) +
  labs(x = "Time(Month)",
       y = "Current Price",
       color = "Vendor") +
  theme_minimal() 
```

>>>>

---
title: "Pricing Approaches for Green Tea Products"
subtitle: "A Study of Canadian Grocery Retailers"
author: 
  - David Qi
  - Haobo Ren
  - Xinrui Xie
  - Ruikang Wang
  - Sakura Hu
thanks: "Code and data are available at: https://github.com/UTDQi/grocery_analysis"
date: today
date-format: long
abstract: "This study uses canadian grocery price data to analyzes the pricing strategies of green tea-related products across grocery stores in Canada. We finds T&T offers a mix of premium and affordable teas, targeting its Asian customer base, while Walmart maintains low prices through economies of scale. Loblaws uses dynamic pricing and promotions to attract budget-conscious consumers. These strategies reflect different approaches to catering to diverse consumer segments."
format: pdf
number-sections: true
toc: true
bibliography: references.bib
---

@@

library(tidyverse)
library(ggplot2)
Sys.setlocale("LC_ALL", "English")

@@

## Overview
[@fig-PriceVsVendor] is a graph showing the overall distribution for price of green tea related products for each vendor. The term average price refers to the mean price of a product observed over the time where data is available.
Most vendors exhibit a right-skewed distribution in green tea related product prices, with the majority priced on the lower end of the spectrum. This pattern suggests that, while there are some high-priced teas, they are relatively uncommon compared to more affordable options.
```{r}
#| label: fig-PriceVsVendor
#| fig-cap: Distribution of Average Green Tea Related Product Prices by Vendor
#| include: true
#| echo: false
#| warning: false
#| message: false

@@

```{r}
#| label: fig-ChangeInGinsengLemon
#| fig-cap: Comparing Price Change of "Lipton Ginseng Lemon Green Tea 72 Counts" Across 3 Vendors
#| include: true
#| echo: false
#| warning: false
#| message: false

# Ensure `nowtime` is in datetime format and `current_price` is numeric
price_change$nowtime <- as.POSIXct(price_change$nowtime)
price_change$current_price <- as.numeric(price_change$current_price)
price_change$nowtime <- as.Date(price_change$nowtime)

ggplot(price_change, aes(x = nowtime, y = current_price, color = vendor)) +
  geom_point(alpha = 0.6) +
  labs(x = "Time",
       y = "Current Price",
       color = "Vendor") + 
  theme_minimal()
```
